Unified Linear Speedup Analyses of Communication-Efficient Stochastic FedAvg and Nesterov FedAvg

### 2021-07-11 source/main.tex
Update bio
Update on Overleaf.

\newpage
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/bio_zhaonan.jpg}}]{Zhaonan Qu}
Zhaonan Qu is a PhD student at the Department of Economics at Stanford University. His research interest is at the intersection of optimization, machine learning, and causal inference. He received a B.S. in mathematics from Princeton University and an M.A. in mathematics from NYU's Courant Institute.
\end{IEEEbiography}

>>>>

\newpage
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/bio_zhaonan.jpg}}]{Zhaonan Qu}
Zhaonan Qu is a PhD student in the Department of Economics at Stanford University. His research interest is at the intersection of optimization, machine learning, and causal inference. He received a B.S. in mathematics from Princeton University and an M.A. in mathematics from NYU's Courant Institute.
\end{IEEEbiography}
